Malacology: A Programmable Storage System

### 2016-10-13 paper/paper.tex
paper: more mantle eval touchup
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
Performance profiles of a single sequencer running in a resource constrained
environment show the benefits of using the load balancing interface.  ``1
Sequencer Baseline'' is the throughput of one sequencer on an underloaded
physical server; the other curves show how load balancing affects the
throughput of one sequencer when sequencers for other logs are co-located on
the same physical server.}\label{fig:mantle-seq-thruput}
\end{figure}

@@

We use a balancer policy specifically designed for multiple sequencers. The
balancer aggressively sheds half its load to the next server as soon as it can.
It is based off the ``Greedy Spill Even" approach in the
Mantle~\cite{sevilla:sc15-mantle} paper but is reproduced in
Figure~\ref{listing:greedy-spill} for the reader's convenience. An MDS is a
physical server capable of housing a sequencer.

\begin{figure}[]
\begin{lstlisting}
  -- Metadata server load
  mdsload = MDSs[i]["all"]

  -- When policy
  if MDSs[whoami]["load"]>.01 and 
    MDSs[whoami+1]["load"]<.01 then

  -- Where policy
  targets[whoami+1]=allmetaload/2
\end{lstlisting}
\caption{The sequencer balancing policy that works best for bursty workloads.
\label{listing:greedy-spill}}
\end{figure}

@@

Figure~\ref{fig:mantle-seq-thruput} shows a performance profile of one of the
sequencers as the load balancing interface migrates sequencers around the
cluster to alleviate load.  Each curve shows the throughput (\(y\) axis) over
time (\(x\) axis).  ``1 Sequencer Baseline'' is the performance of one sequencer
on one physical server serving 7 clients - there are no other sequencers or
logs in the system and the curve represents the maximum throughput of a
sequencer on an underutilized physical server.  ``No Balancing" adds a
second sequencer of equal load to the same physical server with the intent of
overloading the single physical server; recall that the throughput for this
second sequencer is omitted. Compared to the baseline, the overloaded physical
server with 2 sequencers has more than a 2\(\times\) throughput degradation.
The stability of throughput curves (i.e. the variation on the \(y\) axis) indicate which sequencers
are on overloaded physical servers.  ``1 Sequencer Baseline" is the best
performance for this particular workload because there is no contention.
Performance is stable and the MDS is under-loaded because we do not see the
spike at the end like the other curves.  ``No Balancing" shows an
overloaded sequencer because the performance of the monitored sequencer is low
and unstable (high variation in performance).

The last two curves of Figure~\ref{fig:mantle-seq-thruput} show the performance
improvements when sequencers are load balanced across the cluster. Both curves
show the throughput of one of the sequencers when a second sequencer is
running on the same physical server. The load balancing policies differ by the threshold at which they start balancing:
``Sequencer Policy" starts balancing immediately and ``Conservative
Policy" waits for 120 seconds before migrating sequencers.

>>>>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
load balancing interface alleviates load for multiple sequencers in
resource-constrained environments.  ``Underloaded (Baseline)'' is the
throughput of one sequencer running alone on a cluster; the other curves show
how load balancing affects the throughput of one sequencer when sequencers for
other logs are initially co-located on the same physical server (i.e. an
"Overloaded" environment).}\label{fig:mantle-seq-thruput}
\end{figure}

@@

We use a balancer policy specifically designed for multiple sequencers. The
balancer aggressively sheds half its load to the next server as soon as it can.
It is based off the ``Greedy Spill Even" approach in the
Mantle~\cite{sevilla:sc15-mantle} paper but is reproduced in
Figure~\ref{listing:greedy-spill} for the reader's convenience. Each line of
code uses variables exposed by the Mantle API and is executed as a callback by
Mantle.  ``Server load" lets the administrator control what metric constitutes
load on a server; ``i" is a variable used by Mantle to iterate over servers and
``req\_rate" is a metric based on the exponenential decay of the request rate.
``When policy" is used by Mantle to set a conditional for kicking off migration;
in this case, the cluster migrates load if the current server, ``whoami", has
load (\texttt{>0.1}) and the next server (physical servers have ``ranks") has a
small amount load (\texttt{<0.1}). Finally, the ``where policy" is used by
Mantle to determine how much load to shed. The policy fills in a ``targets"
array to tell the migrator how much load to send to each server; in this case,
we shed half of the current load to the next server. The unit of load is a
single sequencer for a ZLog log.

\begin{figure}[]
\begin{lstlisting}
  -- Server load
  load = server[i]["req_rate"]

  -- When policy
  if server[whoami]["load"]>.01 and 
    server[whoami+1]["load"]<.01 then

  -- Where policy
  targets[whoami+1]=load/2
\end{lstlisting}
\caption{The sequencer balancing policy that works best for bursty workloads. 
\label{listing:greedy-spill}}
\end{figure}

@@

Figure~\ref{fig:mantle-seq-thruput} shows a performance profile of one of the
sequencers as the load balancing interface migrates sequencers around the
cluster to alleviate load.  Each curve shows the throughput (\(y\) axis) over
time (\(x\) axis).  ``Underloaded (Baseline)'' is the performance of one sequencer
on one physical server serving 7 clients - there are no other sequencers or
logs in the system and the curve represents the maximum throughput of a
sequencer on an underutilized physical server.  ``Overloaded: No Balancing" adds a
second sequencer of equal load to the same physical server with the intent of
overloading the single physical server; recall that the throughput for this
second sequencer is omitted. Compared to the baseline, the overloaded physical
server with 2 sequencers has more than a 2\(\times\) throughput degradation.
The stability of throughput curves (i.e. the variation on the \(y\) axis) indicate which sequencers
are on overloaded physical servers.  ``Underloaded (Baseline)" is the best
performance for this particular workload because there is no contention.
Performance is stable and the MDS is under-loaded because we do not see the
spike at the end like the other curves.  ``Overloaded: No Balancing" shows an
overloaded sequencer because the performance of the monitored sequencer is low
and unstable (high variation in performance).

The last two curves of Figure~\ref{fig:mantle-seq-thruput} show the performance
improvements when sequencers are load balanced across the cluster.
The load balancing policies differ by the threshold at which they start balancing:
``Overloaded: Sequencer Policy" starts balancing immediately and ``Overloaded: Conservative
Policy" waits for 120 seconds before migrating sequencers.
